### 2022-11-14 NSF2022/Description/summary.tex
yny 1114c

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling, analysis and numerical simulations of
collective dynamics and self-assembly arising from attractive
interactions between dipolar/nematic particles in a suspension. 
%
%One example is the organization of lipids and proteins in vesicles, which is crucial
%to design effective drug carriers. 
%
Physicists model such a self-assembly
using particles possessing a biphasic material label on either half,
with one more hydrophobic than the other. Hydrophobic surfaces
experience a nonadditive long-range attraction called the hydrophobic
force. This force is a major source of nonspecific interactions in
biology and soft matter. Despite its ubiquity, theoretical developments
explaining its basic underlying principles have come relatively late.
Motivated by its broad applicability, the PIs recently developed a novel
and intuitive mathematical model, called the hydrophobic attraction
potential model, based on the linear response of water to surface
perturbations. This model was used to show, for the first time,
self-assembly of such bipolar particles into vesicle-like structures
using moving domain elliptic partial differential equations.

@@

The PIs propose to apply their hydrophobic attraction potential model to
more general self-organization dynamics. They aim to generalize the
linear-response model to more general hydrophobic interactions, and
numerically implement these interactions using integral equation
formulations. Finally, they will develop a coarse-grained model based on 
the kinetic theory to investigate the rheological properties of the assembly of 
particles with tunable hydrophobicity. The unifying
aspects of the project are establishing a platform for efficiently
simulating the collective dynamics at large scales, and the focusing on
rigorous, mathematical analysis of the underlying model equations and
complicated geometries. The project supports undergraduate and graduate
student collaborators.

>>>>

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling, analysis and numerical simulations of
collective dynamics and self-assembly arising from attractive
interactions between dipolar/nematic particles in a suspension. 
%
%One example is the organization of lipids and proteins in vesicles, which is crucial
%to design effective drug carriers. 
%
Physicists model such a self-assembly
using particles possessing a biphasic material label on either half,
with one more hydrophobic than the other. Hydrophobic surfaces
experience a non-additive long-range attraction called the hydrophobic
force. This force is a major source of nonspecific interactions in
biology and soft matter. Despite its ubiquity, theoretical developments
explaining its basic underlying principles have come relatively late.
Motivated by its broad applicability, the PIs recently developed a novel
and intuitive mathematical model, called the hydrophobic attraction
potential model, based on the linear response of water to surface
perturbations. This model was used to show, for the first time,
self-assembly of such bipolar particles into vesicle-like structures
using moving domain elliptic partial differential equations.

@@

The PIs propose to analyze the near-linear elliptic PDEs, develop fast and accurate numerical schemes, 
and apply their hydrophobic attraction potential model to
more general self-organization dynamics. They aim to generalize the
linear-response model to  a wider class of hydrophobic interactions, and
numerically implement these interactions using integral equation
formulations. Finally, they will develop a coarse-grained model based on 
the kinetic theory to investigate the rheological properties of the assembly of 
particles with tunable hydrophobicity. The unifying
aspects of the project are establishing a platform for efficiently
simulating the collective dynamics at large scales, and the focusing on
rigorous, mathematical analysis of the underlying model equations and
complicated geometries. The project supports undergraduate and graduate
student collaborators.
